---
title: "R Markdown and Maps!"
author: "Luis Eduardo San Martin"
date: "February 12th, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Used

Here is the data I used in this analysis:

- Library data (points)
- Community area data (polygons)

Why I used this data?

1. They have different geometries
2. I could do an interesting, challenging exercise with it
3. They produced a cool map

## Maps we produced - reading map images



## Loading data and plotting
```{r include = FALSE}
library(sf)
library(ggplot2)
library(dplyr)
```
Loading data:
```{r, echo = FALSE, warning = FALSE, message = FALSE}
libraries <- st_read("https://data.cityofchicago.org/resource/psqp-6rmg.geojson")
areas <- st_read("https://data.cityofchicago.org/resource/igwz-8jzy.geojson")
```
Plotting: Chicago community areas and public libraries
```{r}
ggplot() +
  geom_sf(data = areas) +
  geom_sf(data = libraries)
```

Highlighting community areas without maps:
```{r }
intersects <- st_intersects(areas, libraries)
no_lib <- filter(areas, lengths(intersects) == 0)
ggplot() +
  geom_sf(data = areas) +
  geom_sf(data = no_lib, fill = "red") +
  geom_sf(data = libraries)